---
title: "Developing with rofi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Developing with rofi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

Okay, so it is time to start writing some `rofi` code of your own. As
previously mentioned, `rofi` is quite opinionated about directory
structure and coding style that should make it easier for those just
starting out to do just that, get started. 

We believe that R code is best expressed in functions. A function is
basically a reusable piece of code, that uses some input (provided in
the form of arguments) to produce some output. Often, functions also
work in isolation and without side effects, meaning that whatever
happens inside a function does not affect the environment outside of
that function. 

We think that there should be one function per file (with few
exceptions, for example if you want to collect many very short and
related functions in one file). This style makes it easier for several
persons to work together on the same codebase.

So, let's create your first function. At some point you probably want
to select just a few of all the variables in the complete dataset,
because you do not need all of them for your particular project. Let's
say that this function "prepares" the data for further analyses. So:

```{r, eval = FALSE}
library(rofi)
create_function("Prepare data")
```

This should create a file called `prepare_data.R` in the directory
`functions` and open that file in your editor. It should look
something like this:

```{r, eval = FALSE}
#' Prepare Data
#'
#' Write a short description of your function here 
#' @param x Describe argument x here 
#' @export 
prepare_data <- function(x) {
    ## Replace with the contents of your function
    y <- x + 1
    return (y)
}
```

Now. Replace "Write a short description of your function here" with a
short description of what your function does (maybe you wonder what
the weird "#'" and "@param" and so on comes from. Those are from
`roxygen`, a way of documenting R code for packages. See
https://r-pkgs.org/man.html for details). You could for example write
"Prepare my dataset for analysis by selecting only required
variables". The file would then look like this:

```{r, eval = FALSE}
#' Prepare Data
#'
#' Prepare my dataset for analysis by selecting only required variables
#' @param x Describe argument x here 
#' @export 
prepare_data <- function(x) {
    ## Replace with the contents of your function
    y <- x + 1
    return (y)
}'
```

The "@param" denotes documentation of a single argument, in this case
called `x`. In this case `x` is a very uninformative argument name, so
let's rename it to something more informative and intuitive, for
example `dataset`. Let's also describe this argument, for example "The
complete dataset", and replace `x` in the function definition with
`dataset`:

```{r, eval = FALSE}
#' Prepare Data
#'
#' Prepare my dataset for analysis by selecting only required variables
#' @param dataset The complete dataset.
#' @export 
prepare_data <- function(dataset) {
    ## Replace with the contents of your function
    y <- x + 1
    return (y)
}
```

Finally, let's do something useful with this function, namely
selecting only the variables that we're going to use and return this
smaller dataset:

```{r, eval = FALSE}
#' Prepare Data
#'
#' Prepare my dataset for analysis by selecting only required variables
#' @param dataset The complete dataset.
#' @export 
prepare_data <- function(dataset) {
    variables.to.include <- c("age", "sex", "sbp", "hr", "rr", "niss")
    prepared.dataset <- dataset[, variables.to.include]
    return (prepared dataset)
}
```

Now that we have this function, let's go ahead and add it to our main
script. Open the file `main.R` and add this function to where you want
to use it. For example just after importing your data:

```{r, eval = FALSE}
## Import data
data <- import_data(test = TRUE)

## Prepare data
prepared.data <- prepare_data(data)
```

Note that if you give your function explicit names the comments are
quite unnecessary, the function names themselves indicate what the
functions do, and your main script becomes a roadmap or analysis plan
showing what happens when, but with the bulk of the code contained in
functions, kept in separate files.
